Topic modeling bla bla

### 2017-06-03 thesis_report/draft_thesis.tex
Auto wrap

Many applications of if topic modeling also eliminate from the vocabulary so-called 
“stop” words. These are words that are common in most documents and do not correspond 
to any particular subject matter. They include pronouns (you, he, it), connectives 
(and, because, however), prepositions (to, of, before), and auxiliaries 
(have, been, can, should). Stop words may also include generic nouns 
(amount, part, nothing) and verbs (do, have). A collection of documents is 
represented as a two-dimensional matrix where each row describes a document 
and each column corresponds to a word. Each entry in this matrix is an integer count; 
most entries are zero. It makes sense to view each column as a feature.

@@

\subsection{The Multinomial Distribution}

Once we have a representation for individual documents, the natural next step 
is to select a model for a set of documents. It is important to understand the 
difference between a representation and a model. A representation is a way of 
encoding an entity as a data structure. A model is an abstraction of a set of 
entities, for example a probability distribution. Given a training set of documents, 
we will choose values for the parameters of a probabilistic model that make the 
training documents have high probability. Then, given a test document, we can 
evaluate its probability according to the model. The higher this probability is, 
the more similar the test document is to the training set.

@@

\begin{equation}
p(x;\theta) = \left(\frac{n!}{\prod\limits_{j=1}^m x^j!}\right)\left(\prod\limits_{j=1}^m \theta_j^{x_j}\right)
\end{equation}

>>>>

Many applications of if topic modeling also eliminate from the vocabulary so-
called “stop” words. These are words that are common in most documents and do
not correspond to any particular subject matter. They include pronouns (you,
he, it), connectives (and, because, however), prepositions (to, of, before),
and auxiliaries (have, been, can, should). Stop words may also include generic
nouns (amount, part, nothing) and verbs (do, have). A collection of documents
is represented as a two-dimensional matrix where each row describes a document
and each column corresponds to a word. Each entry in this matrix is an integer
count; most entries are zero. It makes sense to view each column as a feature.

@@

\subsection{The Multinomial Distribution}
Once we have a representation for individual documents, the natural next step
is to select a model for a set of documents. It is important to understand the
difference between a representation and a model. A representation is a way of
encoding an entity as a data structure. A model is an abstraction of a set of
entities, for example a probability distribution. Given a training set of
documents, we will choose values for the parameters of a probabilistic model
that make the training documents have high probability. Then, given a test
document, we can evaluate its probability according to the model. The higher
this probability is, the more similar the test document is to the training set.

@@

\begin{equation}
p(x;\theta) = \left(\frac{n!}{\prod\limits_{j=1}^m x^j!}\right)\left
(\prod\limits_{j=1}^m \theta_j^{x_j}\right)
\end{equation}
